\input{preamble.tex} 
\namesection{\textbf{Tahsin} \textbf{Ridwan} Pulok}{}{ \urlstyle{same}\href{}{ } | \\
    \href{mailto:taksin.pulok@gmail.com}{taksin.pulok@gmail.com} | +880 1785 051566 | Zigatola, Dhanmondi, Dhaka- 1209.\\}

\begin{minipage}[t]{0.36\textwidth}
    \section{Education} % if data available
      \subsection{North South University}
      \summaryPoints{Bachelor of Architecture (B.Arch) | GPA: 2.7/4.0 (82\%) }
      \subHeading{Graduated Jan 2021}
    \sectionsep

    \section{Relevant Courses} % if data available
      
    \sectionsep

    \section{Skills} 
    \subHeading{Tools}
      Construction Documents \textbullet{} BOQ Preparation \textbullet{} \textbf{AutoCAD} \textbullet{} \textbf{SketchUp} \textbullet{} 3ds Max \textbullet{} \textbf{Revit} \textbullet{} Rhino \textbullet{} Creating computer-generated 3D models and rendering \textbullet{} Prepared 3D models for necessary representation and implementation \textbullet{} Prepared 3D model of architecture and landscape of the project \textbullet{} Prepared 3D models and renderings for visual representation \textbullet{} Prepared 3D models and renders \\
    \skillsVSpace

    \subHeading{Soft Skills}
      Communication \textbullet{} Teamwork \textbullet{} Independent Work \textbullet{} Proficient in diverse digital design software \textbullet{} Preparation of preliminary and detailed architectural drawings \textbullet{} Prepared technical and detailed drawings \textbullet{} Prepared working drawings for residential, commercial and interior projects \textbullet{} Prepared detailed drawings for interior projects \textbullet{} Arranged RAJUK sheets and layouts \\
    \skillsVSpace
    \sectionsep

    \section{VOLUNTEER} % if data available
      
    \sectionsep

    \section{AWARDS} % if data available
      
    \sectionsep

    \section{REFERENCES} % if data available
      \subsection{Shaila Joarder}
      \subHeading{Associate Professor | Department of Architecture, North South University}
      - Email: shaila.joarder@northsouth.edu \newline
      - 
    \sectionsep

    \subsection{Fariha Yasmin Faruque}
      \subHeading{Architectural Designer | ProWise Engineering Inc.}
      - Email: fariha.faruque@prowise.ca \newline
      - 
    \sectionsep

    \subsection{Krishno Sen}
      \subHeading{Senior Analysts | Leaving No One Behind (LNOB), BRAC Bangladesh}
      - Email: krishno.sen@brac.net \newline
      - 
    \sectionsep
      
    \section{ACTIVITIES} % if data available
      
    \sectionsep

\end{minipage} \hfill \begin{minipage}[t]{0.63\textwidth}

    \section{Career Goal} 
      \betweensummaryPointsionVSpace
      \subHeading{Highly motivated Architect with a demonstrated ability to translate design concepts into detailed construction documents and 3D visualizations, seeking to leverage expertise in AutoCAD, SketchUp, and Revit at Shibori Ltd. to contribute to innovative and sustainable design solutions.}
    \sectionsep

  \section{Work Experience}
    \experienceTitle{Architect}
    \summaryPoints{ }
    \subHeading{RSB Properties Ltd. | Oct 2022 - Jul 2023 (9 months)}
    
    \vspace{15pt} % Hacky fix for awkward extra vertical space only for the first section, otherwise, \vspace{5pt} is sufficient
    
    \begin{tightemize}
      \item Prepared design solutions and construction documents, applying problem-solving skills to address design challenges while meeting project schedules.
      \item Collaborated effectively with cross-functional teams, including engineers and contractors, to ensure seamless project execution.
      \item Utilized strong communication skills to present design concepts and technical drawings to clients and stakeholders.
      
    \end{tightemize}
  \sectionsep

    \experienceTitle{Architectural Intern}
    
    \subHeading{Tania Karim, Nurur Rahman Khan and Associates (TKNRK) | Jun 2019 - Sep 2019 (3 months)}
    \vspace{5pt}
    \begin{tightemize}
      \item Contributed to the design and development of architectural drawings, applying knowledge of building codes and regulations.
      \item Demonstrated proficiency in using software for 3D visualization and rendering, enhancing the presentation of design concepts.
      \item Gained practical experience in preparing construction documents, including BOQs, contributing to the successful execution of projects.
      
    \end{tightemize}
  \sectionsep

    \experienceTitle{Technical Trainee on Reasonable Accommodation and Accessibility}
    
    \subHeading{Humanity \& Inclusion (HI), Centre for the Rehabilitation of the Paralysed (CRP) | Jan 2022 - Jul 2022 (6 months)}
    \vspace{5pt}
    \begin{tightemize}
      \item Developed technical drawings and 3D models that met accessibility standards and guidelines.
      \item Collaborated with a team to assess and analyze the accessibility of built environments.
      \item Utilized design skills to propose and present solutions that promoted inclusivity and accessibility.
      
    \end{tightemize}
  \sectionsep

  \section{Project Experience}
    
  \end{minipage}
\end{document}