\section{Experience}
\customTitle{ATS Pass AI}
    \summaryPoints{Python | Multiagent | AI}
    \roleAndTimeline{Resume Automation Tool - January 2024 - Present}

    \shortDescription{Led the development of an AI-driven project, integrating CrewAI to automate tailored resume creation for enhanced job search efficiency.}

    \begin{tightemize}
        \item Engineered a system that personalizes resumes using AI, achieving over 85\% keyword alignment with job descriptions for optimal \textbf{ATS optimization}.
        \item Developed a \textbf{multiagent} system for collaborative resume writing, fostering teamwork and enhancing resume quality.
        \item Implemented \textbf{Python} scripts to automate resume generation, streamline processes, and improve efficiency.
        \item See my \href{https://github.com/vmsaif/ats-pass-ai}{\ul{work}} on the development of a generative AI-driven system.
    \end{tightemize}

\customTitle{AI Pathfinding}
    \summaryPoints{Java | CI/CD | A* Algorithm}
    \roleAndTimeline{AI-Driven Game - September 2023 - December 2023}

    \shortDescription{Developed an AI-driven game utilizing the A* algorithm to enhance user engagement and problem-solving skills.}

    \begin{tightemize}
        \item Designed and implemented an \textbf{A* algorithm} for efficient pathfinding, showcasing expertise in AI techniques.
        \item Utilized **Java** for game development, demonstrating proficiency in a programming language widely used in AI applications.
        \item Implemented **CI/CD** practices, ensuring continuous integration and delivery of game updates.
        \item See my \href{https://github.com/vmsaif/ant-path-finding-using-A-Star-algorithm}{\ul{project}} on the development of an AI-driven game utilizing the A* algorithm to enhance user engagement.
    \end{tightemize}
