\section{Experience}
  \customTitle{ATS Pass AI}
      \summaryPoints{Python | AI | RAG | SQL}
      \roleAndTimeline{Resume Automation Tool - Jan 2024 - Present}

      \shortDescription{Developed an AI-powered resume builder application leveraging Gemini Pro and LangChain.}

      \begin{tightemize}
          \item Developed an AI-powered resume builder application designed to optimize resumes for Applicant Tracking Systems (ATS), improving keyword matching.
          \item Utilized advanced language models, including Gemini Pro and LangChain, for enhanced natural language processing and resume generation to improve readability and impact.
          \item Implemented a Multi-agent System powered by CrewAI to facilitate efficient data extraction from user inputs and tailor resumes accordingly for ATS compatibility.
          \item Achieved an impressive 85\% keyword matching rate with user-provided job descriptions, significantly increasing the chances of passing ATS screenings.
          \item See my github \href{https://github.com/vmsaif/ats-pass-ai}{\ul{profile}}.
      \end{tightemize}

  \customTitle{Programming Mentor}
      \summaryPoints{Python | Java | Soft Skills}
      \roleAndTimeline{Self-Employed - Feb 2023 - Dec 2023}

      \shortDescription{Provided private tutoring sessions focused on Python and Java programming, incorporating debugging techniques and software installation.}

      \begin{tightemize}
          \item Delivered personalized one-on-one programming tutoring sessions tailored to the student's learning style and pace, demonstrating strong communication and interpersonal skills.
          \item Provided hands-on, practical programming experience using Python and Java, covering fundamental concepts, debugging techniques, and software installation, enhancing problem-solving skills.
          \item Successfully imparted knowledge and fostered the student's programming skills through adaptive teaching methods and personalized guidance.
      \end{tightemize}