\section{Experience}
\betweenProjectsVSpace
\experienceTitle{Architect}
\summaryPoints{| AutoCAD | SketchUp | 3DS Max}
\subHeading{RSB Properties Ltd. - October 2022 - July 2023}
\betweenSummaryPointsVSpace
Developed architectural designs, 3D models, and construction documents using Revit, AutoCAD, and SketchUp. Managed project progress, ensured compliance with building codes, and collaborated with cross-functional teams to deliver high-quality designs.
\vspaceForFirstProject
\begin{tightemize}
\item Prepared detailed construction drawings for residential, commercial, and landscaping projects.
\item Created 3D models and renderings for design visualization and presentation.
\item Conducted site surveys, analyzed existing structures, and prepared renovation plans.
\item Coordinated with contractors and engineers to ensure project specifications were met.
\end{tightemize}
\betweenProjectsVSpace
\experienceTitle{Technical Trainee on Reasonable Accommodation and Accessibility}
\summaryPoints{| AutoCAD | SketchUp | 3DS Max}
\subHeading{Humanity \& Inclusion (HI), Centre for the Rehabilitation of the Paralysed (CRP) - January 2022 - July 2022}
\betweenSummaryPointsVSpace
Utilized AutoCAD, SketchUp, and 3DS Max to design and modify accessible environments for individuals with disabilities. Conducted assessments, prepared technical drawings, and collaborated with occupational therapists to ensure compliance with accessibility standards.
\vspaceForOtherProject
\begin{tightemize}
\item Designed ramps, elevators, and other accessibility features to improve mobility and safety.
\item Prepared technical drawings and specifications for construction and renovation projects.
\item Conducted site surveys to assess existing conditions and identify potential accessibility barriers.
\item Assisted in developing training materials and workshops on accessibility best practices.
\end{tightemize}
\betweenProjectsVSpace
\experienceTitle{Project Architect}
\summaryPoints{| AutoCAD | SketchUp | 3DS Max}
\subHeading{Integrated Design (Project: Visualization of BSRM Tunnel Service Area) - September 2021 - December 2021}
\betweenSummaryPointsVSpace
Developed 3D architectural models and visualizations for a proposed tunnel service area. Collaborated with engineers and designers to create a visually appealing and functional design. Utilized AutoCAD, SketchUp, and 3DS Max to produce high-quality renderings and animations.
\vspaceForOtherProject
\begin{tightemize}
\item Created detailed 3D models of the architecture, landscape, and surrounding environment.
\item Produced realistic renderings and animations to showcase the design concept and functionality.
\item Presented design proposals to clients and stakeholders, incorporating their feedback into the final design.
\item Coordinated with the project team to ensure the design met all technical and aesthetic requirements.
\end{tightemize}
\betweenProjectsVSpace
\experienceTitle{Architectural Intern}
\summaryPoints{| AutoCAD | SketchUp | Revit}
\subHeading{Tania Karim, Nurur Rahman Khan and Associates (TKNRK) - June 2019 - September 2019}
\betweenSummaryPointsVSpace
Gained hands-on experience in architectural design and documentation. Assisted senior architects in preparing working drawings, construction documents, and presentations. Utilized AutoCAD, SketchUp, and Revit to develop technical drawings and 3D models.
\vspaceForOtherProject
\begin{tightemize}
\item Contributed to the design and development of residential and commercial projects.
\item Prepared construction drawings, including floor plans, elevations, and sections.
\item Created 3D models to visualize design concepts and communicate design intent.
\item Participated in client meetings and presentations, presenting design ideas and addressing queries.
\end{tightemize}
\betweenProjectsVSpace
\experienceTitle{Junior Designer}
\summaryPoints{| AutoCAD | SketchUp | Revit}
\subHeading{Simple Interiors - April 2017 - December 2017}
\betweenSummaryPointsVSpace
Utilized AutoCAD, SketchUp, and Revit to design and visualize interior spaces. Collaborated with clients to understand their requirements and create functional and aesthetically pleasing designs. Prepared technical drawings, 3D models, and renderings to present design concepts.
\vspaceForOtherProject
\begin{tightemize}
\item Designed interior layouts, furniture plans, and lighting schemes for residential and commercial projects.
\item Created 3D models and renderings to showcase design ideas and material selections.
\item Prepared construction drawings, including floor plans, elevations, and details.
\item Assisted in project management tasks, including client communication and coordination with contractors.
\end{tightemize}
\betweenProjectsVSpace
\experienceTitle{Graphic Designer}
\summaryPoints{| Photoshop | Illustrator}
\subHeading{UniAssist Global Education - September 2019 - December 2019}
\betweenSummaryPointsVSpace
Designed marketing materials, including brochures, posters, and social media graphics. Collaborated with the marketing team to develop visually appealing and effective promotional materials. Utilized Photoshop and Illustrator to create high-quality designs and artwork.
\vspaceForOtherProject
\begin{tightemize}
\item Designed and produced marketing materials for Education Expo 2019.
\item Created social media graphics, banner ads, and other promotional materials.
\item Collaborated with文案 and marketing professionals to ensure designs aligned with campaign goals.
\item Assisted in the development of the company's brand identity and visual guidelines.
\end{tightemize}