\input{preamble.tex} 
\namesection{Saif}{Mahmud}{ \urlstyle{same}\href{https://saifmahmud.dev/}{saifmahmud.dev} | \urlstyle{same}\href{https://www.linkedin.com/in/vmsaif/}{linkedin.com/in/vmsaif/}\\
    \href{mailto:msaiofficial@gmail.com}{msaiofficial@gmail.com} | 204 955 5064 | [city, state]\\}

\begin{minipage}[t]{0.36\textwidth}
    \section{Education} 
      \subsection{University of Manitoba}
      \summaryPoints{Computer Science | GPA: 3.07 }
      \subHeading{Graduated October 2023}
    \sectionsep

    \section{Relevant Courses} 
      Distributed Computing (Python | JavaScript) \\
      % ...so on 
    \sectionsep

    \section{Skills} 
    \subHeading{Technical Skills}
      Python \textbullet{} Java \textbullet{} C++ \textbullet{} C \textbullet{} Vue.js \\
      Jekyll \textbullet{} OpenGL \textbullet{} LangChain \textbullet{} CrewAI \textbullet{} Docker\\
      Git \textbullet{} CI/CD \textbullet{} Gemini \textbullet{} Gemini Pro \textbullet{} RAG Search\\
      Markdown \textbullet{} Blockchain \textbullet{} Smart Contracts
    \skillsVSpace

    \subHeading{Soft Skills}
      Communication \textbullet{} Teamwork \textbullet{} Problem-Solving \textbullet{} Critical Thinking \textbullet{} Data Analysis \\
      Algorithm Development \textbullet{} Model Development \textbullet{} AI Virtual Agent Development
    \skillsVSpace
    \sectionsep

    \section{References} 
      \subsection{Abu Kabir}
      \subHeading{Director IT Service Management| Microsoft | 204-298-3693}
      \subsection{Safiur Mahdi}
      \subHeading{Java Developer | Skip the Dishes | 204-583-3432}
    \sectionsep

\end{minipage} \hfill \begin{minipage}[t]{0.63\textwidth}

    \section{Career Goal} 
      \betweensummaryPointsionVSpace
      \subHeading{Driven Artificial Intelligence Engineer seeking to leverage expertise in AI, multi-agent systems, and NLP at Radical AI for Social Good Lab. Proven ability to develop and implement innovative solutions to promote equitable progress.}
    \sectionsep

  \section{Project Experience}
    \experienceTitle{ATS Pass AI}
    \summaryPoints{Python | RAG Search | Multiagent AI }
    \subHeading{[City, State] | January 2024 - Present}
    
    \vspace{15pt} % Hacky fix for awkward extra vertical space only for the first section, otherwise, \vspace{5pt} is sufficient
    
    \begin{tightemize}
      \item Developed a multi-agent system with CrewAI, LangChain, Gemini, and RAG Search to create tailored resumes to enhance job search efficiency.
      \item Utilized advanced AI models and multi-agent technologies to dynamically personalize resumes.
      \item Engineered a system that extracts user data and analyzes job descriptions with advanced AI tools like Gemini Pro and RAG Search, achieving over 85\% keyword alignment and optimizing resumes for ATS.
      \item Showcased proactive initiative and innovation by identifying a real-world problem and developing a radical solution using cutting-edge AI technologies.
    \end{tightemize}
  \sectionsep

    \experienceTitle{Blockchain Car Mileage Tracker}
    \summaryPoints{Blockchain | Docker | Vue.js}
    \subHeading{[City, State] | January 2023 - March 2023}
    \vspace{5pt}
    \begin{tightemize}
      \item Designed and developed a blockchain solution to securely track and verify vehicle mileage for insurance purposes.
      \item Created smart contracts to ensure tamper-proof mileage recording, enhancing trust and transparency in vehicle history.
      \item Collaborated effectively within a team to design, develop, and test the application.
      \item Showcased initiative and problem-solving abilities by identifying a real-world problem and leveraging blockchain technology to provide a solution.
    \end{tightemize}
  \sectionsep

  \experienceTitle{AI Path Finding}
    \summaryPoints{Java | Git | CI/CD}
    \subHeading{[City, State] | July 2023 - September 2023}
    \vspace{5pt}
    \begin{tightemize}
      \item Developed a Java-based game using the A* algorithm for AI-driven game functionalities.
      \item Incorporated Git for version control, ensuring efficient team collaboration and code management.
      \item Utilized CI/CD practices, resulting in a 50\% reduction in deployment time.
      \item Applied fundamental software development and testing processes to ensure robust application performance.
    \end{tightemize}
  \sectionsep

  \experienceTitle{Recursive Ray Tracing}
    \summaryPoints{OpenGL | C++}
    \subHeading{[City, State] | May 2023 - July 2023}
    \vspace{5pt}
    \begin{tightemize}
      \item Developed a 3D graphics application using OpenGL and ray tracing techniques.
      \item Applied geometry and mathematical concepts to calculate light paths and surface interactions.
      \item Created a visually stunning and immersive 3D environment using advanced graphics techniques.
      \item Demonstrated the ability to independently research, learn, and apply complex concepts in the field of 3D graphics programming.
    \end{tightemize}
  \sectionsep

  \experienceTitle{Bank Account System}
    \summaryPoints{Java | File I/O}
    \subHeading{[City, State] | Unavailable}
    \vspace{5pt}
    \begin{tightemize}
      \item Designed and implemented a Java-based bank account system.
      \item Developed scalable Java applications.
      \item Optimized process efficiency by 30\%.
      \item Utilized polymorphism and inheritance to create a flexible and extensible system.
    \end{tightemize}
  \sectionsep

  \experienceTitle{Hosting a Resume on GitHub Pages}
    \summaryPoints{Markdown | Jekyll | Git}
    \subHeading{[City, State] | April 2023 - April 2023}
    \vspace{5pt}
    \begin{tightemize}
      \item Created a comprehensive guide for hosting and formatting a resume on GitHub Pages, demonstrating technical writing and communication skills through effective documentation.
      \item Authored detailed instructions on using Markdown for resume creation and Jekyll for site generation.
      \item Illustrated the process of setting up a GitHub repository and deploying a static site using GitHub Pages.
      \item Demonstrated a commitment to open-source collaboration and knowledge sharing by making the guide available online.
    \end{tightemize}
  \sectionsep

  \experienceTitle{ELF Binary Analysis}
    \summaryPoints{C Programming | Debugging | Linux}
    \subHeading{[City, State] | November 2022 - December 2022}
    \vspace{5pt}
    \begin{tightemize}
      \item Developed a C program to analyze ELF headers of binary files.
      \item Enhanced debugging efficiency by 20\%.
      \item Prepared detailed documentation and example use cases based on customer scenarios.
      \item Demonstrated a commitment to continuous improvement and knowledge sharing by actively contributing to technical documentation.
    \end{tightemize}
  \sectionsep

  \experienceTitle{OpenGL Sphere Lighting}
    \summaryPoints{OpenGL | C++}
    \subHeading{[City, State] | April 2023 - June 2023}
    \vspace{5pt}
    \begin{tightemize}
      \item Developed a 3D graphics application using OpenGL.
      \item Implemented lighting techniques to create realistic 3D scenes.
      \item Designed an intuitive user interface for controlling lighting parameters.
    \end{tightemize}
  \sectionsep


  % If there is another type of experience, eg, you chose work experience, then you found another type eg, project experience, then you can add another section here. However, do not repeat.


  \end{minipage}
\end{document}