\section{Experience}
\customTitle{ATS Pass AI}
    \summaryPoints{Python | RAG Search | CrewAI | LangChain}
    \roleAndTimeline{Resume Automation Tool - January 2024 - Present}

    \shortDescription{Developed a multi-agent system to create tailored resumes using AI and natural language processing.}

    \begin{tightemize}
        \item Developed a multi-agent system to create \textbf{personalized} resumes using \textbf{AI} and \textbf{natural language processing (NLP).}
        \item Utilized advanced \textbf{AI models} and multi-agent technologies to dynamically \textbf{personalize} resumes, demonstrating cutting-edge technical and \textbf{analytical} capabilities.
        \item Project repository available here on \href{https://github.com/vmsaif/ats-pass-ai}{\ul{GitHub}}. 
    \end{tightemize}

\customTitle{AI Path Finding}
    \summaryPoints{Java | A* Algorithm | Git | CI/CD}
    \roleAndTimeline{AI Game Development - Jul 2023 - Sep 2023}

    \shortDescription{Developed a Java-based game leveraging the A* algorithm for AI-driven gameplay.}

    \begin{tightemize}
        \item Developed a Java-based game development project that leveraged the A\* algorithm to create an AI-driven game. 
        \item Utilized Git for version control and CI/CD practices, resulting in a 50\% reduction in deployment time.
        \item Project repository available here on \href{https://github.com/vmsaif/ant-path-finding-using-A-Star-algorithm}{\ul{GitHub}}.
    \end{tightemize}

\customTitle{Connect 4 Game}
    \summaryPoints{Java | AI | Game Dev. | CI/CD}
    \roleAndTimeline{Game Development - February 2023 - April 2023}

    \shortDescription{Developed a digital Connect 4 game featuring AI decision-making on a 6x7 grid.}

    \begin{tightemize}
        \item Developed a digital version of the classic Connect 4 game, facilitating user vs. AI gameplay on a 6x7 grid.
        \item Implemented strategic AI decision-making, enhancing game complexity and player engagement.
        \item Project repository available here on \href{https://github.com/vmsaif/connect4-with-minimax-algorithm-in-java}{\ul{GitHub}}.
    \end{tightemize}
